---
title: "PCOS Charts Example"
lang: "en"
output:
  rmarkdown::html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    css: "style.css"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE, echo = FALSE, warning = FALSE, out.width = "100%", fig.height = 4
)

source("data_prep.R")
```

## 1. Awareness of NISRA

### Current year, `r current_year`

Just under half of respondents (`r heard_of_nisra`%) said they had heard of NISRA before being contacted about the survey.

### Comparison over time

Although there has been a decrease since 2020 and 2021, awareness of NISRA in 2022 is notably higher than in 2019 (35%) and previous years, before the start of the COVID-19 pandemic (Chart 1).

#### Chart 1: Awareness of NISRA (2009-`r current_year`)

```{r Chart 1}
plot_ly(aware_nisra_data,
  x = ~year,
  y = ~pct,
  type = "scatter",
  mode = "lines+markers",
  text = ~ paste0(year, ": ", round_half_up(pct), "%"),
  marker = list(
    size = 8,
    color = "#00205b"
  ),
  line = list(
    width = 4,
    color = "#00205b"
  ),
  hoverinfo = "text",
  name = "Awareness of NISRA"
) %>%
  add_annotations(
    x = ~ year + 0.1,
    y = ~ pct - 3,
    yanchor = "top",
    text = ~ paste0("<b>", round_half_up(pct), "%</b>"),
    showarrow = FALSE,
    font = list(color = "#00205b")
  ) %>%
  layout(
    showlegend = TRUE,
    legend = list(
      x = 0.5,
      xanchor = "center",
      xref = "paper",
      y = -0.1,
      yref = "paper",
      yanchor = "top"
    ),
    font = list(family = "Arial", size = 12),
    xaxis = list(
      title = "",
      showline = TRUE,
      linecolor = "#000000",
      showgrid = FALSE,
      showticklabels = TRUE,
      ticks = "outside",
      tickwidth = 1,
      tickvals = ~ (min(year):max(year)),
      tickmode = "array",
      fixedrange = TRUE
    ),
    yaxis = list(
      title = "",
      showline = TRUE,
      range = c(0, 100),
      linecolor = "#000000",
      showgrid = FALSE,
      fixedrange = TRUE
    ),
    annotations = list(
      list(
        text = "Percentage",
        x = 0,
        xref = "paper",
        xanchor = "center",
        y = 1.05,
        yref = "paper",
        yanchor = "bottom",
        showarrow = FALSE
      )
    ),
    margin = list(t = 50),
    hovermode = "x unified"
  ) %>%
  config(displayModeBar = FALSE)
```

### Comparison by age group

Awareness of NISRA was `r aware_youngest`% among the youngest age group polled (those aged 16 to 24) and `r aware_oldest`% among the oldest age group (aged 75 and over).

#### Chart 2: Awareness of NISRA by Age Group, `r current_year`

```{r Chart 2}

# Exercise 1b
# The exercise uses the plot_ly library to create the html chart
# More information here: https://plotly.com/r/ (Ctrl + click link to follow)

# 1. Run plot_ly() on the aware_by_age data frame with AGE2 on x axis and pct on y axis
# 2. Set type to "bar"
# 3. Name the series "Age Group"
# 4. Set the marker colour to #00205b
# 5. Use the formula `paste0(AGE2, ": ", round_half_up(pct), "%")` to output the hovertext
# 6. Set hoverinfo to "name+text"
# 7. Set texttemplate to "<b>%{y:.0f}</b>"
# 8. Set textposition to "inside"
# 9. Set insidetextanchor to "middle
# 10. Uncomment the layout code below
# 11. Remove the plotly mode bar using `config(displayModeBar = FALSE)`
 
plot_ly(aware_by_age,
  x = ~AGE2,
  y = ~pct,
  type = "bar",
  name = "Age Group",
  marker = list(color = "#00205b"),
  hovertext = ~paste0(AGE2, ": ", round_half_up(pct), "%"),
  hoverinfo = "name+text",
  texttemplate = "<b>%{y:.0f}</b>",
  textposition = "inside",
  insidetextanchor = "middle"
) %>%
  layout(
    font = list(family = "Arial", size = 12),
    legend = list(
      orientation = "h",
      x = 0.5,
      y = -0.05,
      xanchor = "center"
    ),
    yaxis = list(
      title = "",
      range = c(0, 100),
      showline = TRUE,
      fixedrange = TRUE
    ),
    xaxis = list(
      title = "",
      fixedrange = TRUE
    ),
    annotations = list(
      text = "Percentage",
      x = 0,
      xref = "paper",
      xanchor = "center",
      y = 1.05,
      yref = "paper",
      yanchor = "bottom",
      showarrow = FALSE
    ),
    margin = list(t = 50)
  ) %>%
  config(displayModeBar = FALSE)
```
